---
title: "lab-07-simpsons.Rmd"
author: "Renad Faris Al-Shammari" ID:"2201003532"
date: "3 March 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r load_libraries, message=FALSE}
library(tidyverse) 
library(mosaicData)
```


## Exercises


1.  
```{r whickam}
?Whickham
```
    
Your answer: 
The data is observational as the description states that is based on age, smoking and mortality , which are all observable events and not produced via experiments. 

2.  
```{r observations}
nrow(Whickham)
```

Your answer; There are 1.314 observations. As we know every row is an observation. 

3.  

```{r number_variables}
names(Whickham)
```

Your answer: (3)
There are 3 variables , "outcome" ,"smoker" , "age"


```{r var_type}
unique(Whickham$outcome)
unique(Whickham$smoker)
unique(Whickham$age)

```

Your answer:
Using the `unique()` function on the 3 variables we could see that "outcome" only takes Alive or Dead value , which makes it categorical non-ordinal. "smoker" only takes Yes or NO , which also makes it categorical non-ordinal . Age is numerical continues data. 

one of the best ways to visualise categorical data is through the use of bar charts.

```{r plot_outcome}
ggplot(Whickham, aes(x = outcome)) +
  geom_bar()

```


```{r plot_smoker}
ggplot(Whickham, aes(x = smoker)) +
  geom_bar()

```

```{r plot_age}
ggplot(Whickham, aes(x = age)) +
  geom_bar()

```


4. 
I think his health is not good. it is exposed to many substances harmful to the lungs, which lead to the loss of the lungs ability to filter, as well as toxins become confined to the lung and smokers are more susceptible to respiratory infections.
And+
I expect the health will be worser and may be the person will be died after while , if he keeping smoke 
```{r plot_smokeVSincome_1}
ggplot(data=Whickham, aes(x=smoker, y=outcome, color=outcome)) + geom_bar(stat="identity")

```

Knit, commit, and push to github.

5. 

```{r plot_smokeVSincome_2}
Whickham %>%
  count(smoker, outcome)
```
Smoker "732" (NO) = 0.3142077 (Dead) >> (68.6) Alive
Smoker "582" (YES) = 0.2388316 (Alive) >> (76.2) Alive
I doesn't expected this result because now the most died people not smoker.

6.

```{r age_cat}
Whickham <- Whickham %>% mutate(age_cat = case_when(age <= 44 ~ "18-14" , age > 44 & age <= 64 ~ "45-64" , age > 64 ~ "65+"))

```

7. 

```{r plot_smokeVSincome_3}
ggplot(data=Whickham, aes(x=outcome, y=smoker,color=smoker, fill=age_cat)) + geom_bar(stat="identity") +facet_wrap(~age_cat)

```
what changes :
The category of the age it's appear to us and we see the most of dead people is smoker in age (65+)
but in age (45-64) and (18-14)the most dead people is smoker that is relationship between the smoking and heath not clearly but can say that your health will be change to worst if you be smoker and
The category of the Alive  it's appears in the youth's (18-14) age more  than ( 45-64) and 65+ Also the smoker (YES) it's more Alive in the category age it's (18-14) 
I believe that the effects increase with age, unlike those who are young and can resist diseases and live more than the age of adults.


Knit, commit, and push to github.